Wealth dynamics in the presence of network structure and primitive cooperation

### 2019-07-12 manuscript/draftcssa19.tex

More specifically, from statistical physics, we borrow the dynamics: diffusion models and associated first-passage time techniques; from network science, we borrow the structural aspects: Erd\H{o}s-R\'{e}nyi network models; and from non-equlibrium statistical physics, CSS and ACE, we borrow a form of cooperation: the concept of coalescence, institution and coordination.

\section{Model}
The model of cooperative wealth accumulation constructed here is best thought of as a stochastic interacting particle system infused with economic sociological semantics. The particle evolves according to an one dimensional diffusion process with constant drift and is driven by a Brownian noise with boundary condition at the origin corresponding to particle absorption. After crossing a pre-determined threshold in state space.

In this section, we introduce the model used for our simulation study.

>>>>

More specifically, from statistical physics, we borrow the dynamics: diffusion models and associated first-passage time techniques; from network science, we borrow the structural aspects: Erd\H{o}s-R\'{e}nyi network (ER) models; and from non-equlibrium statistical physics, CSS and ACE, we borrow a form of cooperation: the concept of coalescence, institution and coordination.

\section{Model}
The model of cooperative wealth accumulation constructed here is best thought of as a stochastic interacting particle system infused with economic sociological semantics. The particle evolves according to an one dimensional diffusion process with constant drift and is driven by a Brownian noise with boundary condition at the origin corresponding to particle absorption. After crossing a pre-determined threshold in state space, particles above the threshold follow a protocol and coalesce together. In an ensemble of otherwise identical particles, a given particle may coalesce with a subset of other particles. This mixing characteristic is encoded via a graph. Both the conjoined particles and individual particles die upon crossing the origin. This model of interacting diffusing particles can be provided with substantive semantics as follows.

%Might be nice to put a nice table here 
The one dimensional state space of the particle is identified with the wealth of an social actor (agent). We consider a homogeneous population where all agents are required burn their wealth at a constant specified rate in order to survive. In addition, the agents all gain wealth at a constant rate. The resource draining rate and the resource gaining rate are additive and constitute the drift of the diffusion process. The environmental contingency is modeled by a Brownian noise of a specified intensity. Upon crossing a specific wealth threshold, agents can coalesce to form a cooperative unit deciding to pool their resources and their environmental contingencies into a single unit which we call a \textit{proto-institution} (proto). The mixing characteristic of this ensemble is the social network (here ER model).
